A properly labelled proof system for intuitionistic modal logics

### 2019-09-18 caleidoscope/caleidoscope.tex
done completeness section

	%%%%
	In order to continue our proof for the five variants of $\kax$, we display the proof for the axiom $\kax[3]$ which also illustrates the need of having the rule corresponding to $\rn{refl}$:

@@

		$\vlderivation {
			\vlin{\rlabrn{\IMP}}
			{}
			{\Rightarrow \labels{x}{\DIA (A \OR B) \IMP (\DIA A \OR \DIA B)}}
			{\vlin {\llabrn{\DIA}}
				{}
				{\futs xy, \labels{y}{\DIA (A \OR B)} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}
				{\vliin{\llabrn{\OR}}{}{\futs xy, \accs yz, \labels{z}{A \OR B} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}{\vlin {\rlabrn{\OR}}
						{}
						{\futs xy, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}
						{\vlin {\rlabrn{\DIA}}
							{}
							{\futs xy, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}}
							{\vlin {\color{red}{\rn{refl}}}
								{}
								{\futs xy, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}
								{\vlin {\rn{id}}
									{}
									{\futs xy, \futs zz, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}
									{\vlhy {}}}}}}{\vlin {\rlabrn{\OR}}
						{}
						{\futs xy, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}
						{\vlin {\rlabrn{\DIA}}
							{}
							{\futs xy, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}}
							{\vlin {\color{red}{\rn{refl}}}
								{}
								{\futs xy, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}
								{\vlin {\rn{id}}
									{}
									{\futs xy, \futs zz, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}
									{\vlhy {}}}}}}}}
		}$

@@

The proof of $\kax[4]$ shows the need of having the rule corresponding to the frame conditions $\rn{F_1}$:

\kfour

@@

	$\vlderivation {
		\vlin{\rlabrn{\IMP}}
		{}
		{\Rightarrow \labels{x}{\DIA \BOT \IMP \BOT}}
		{\vlin {\llabrn{\DIA}}
			{}
			{x \le y, \labels{y}{\DIA \BOT} \Rightarrow \labels{y}{\BOT}}
			{\vlin {\llabrn{\BOT}}
				{}
				{x \le y, yRz, \labels{z}{\BOT} \Rightarrow \labels{y}{\BOT}}
				{\vlhy {}}}}
	}$

@@

\begin{center}
	$\vlderivation {
		\vlin{\rlabrn{\IMP}}
		{}
		{\Rightarrow \labels{x}{A \AND B \IMP B}}
		{\vlin {\llabrn{\AND}}
			{}
			{x \le y, \labels{y}{A \AND B} \Rightarrow \labels{y}{B}}
			{\vlin {\rn{refl}}
				{}
				{x \le y, \labels{y}{A}, \labels{y}{B} \Rightarrow \labels{y}{B}}
				{\vlin {\rn{id}}
					{}
					{x \le y, y \le y, \labels{y}{A}, \labels{y}{B} \Rightarrow \labels{y}{B}}
					{\vlhy {}}}}}
	}$
\end{center}

>>>>

	%%%%
	In order to continue our proof for the five variants of $\kax$, we display the proof for the axiom $\kax[3]$: %which also illustrates the need of having the rule corresponding to $\rn{refl}$:

@@

		$\vlderivation {
			\vlin{\rlabrn{\IMP}}
			{}
			{\Rightarrow \labels{x}{\DIA (A \OR B) \IMP (\DIA A \OR \DIA B)}}
			{\vlin {\llabrn{\DIA}}
				{}
				{\futs xy, \labels{y}{\DIA (A \OR B)} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}
				{\vliin{\llabrn{\OR}}{}{\futs xy, \accs yz, \labels{z}{A \OR B} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}{\vlin {\rlabrn{\OR}}
						{}
						{\futs xy, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}
						{\vlin {\rlabrn{\DIA}}
							{}
							{\futs xy, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}}
							{\vlin {\rn{refl}}
								{}
								{\futs xy, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}
								{\vlin {\rn{id}}
									{}
									{\futs xy, \futs zz, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}
									{\vlhy {}}}}}}{\vlin {\rlabrn{\OR}}
						{}
						{\futs xy, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}
						{\vlin {\rlabrn{\DIA}}
							{}
							{\futs xy, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}}
							{\vlin {\rn{refl}}
								{}
								{\futs xy, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}
								{\vlin {\rn{id}}
									{}
									{\futs xy, \futs zz, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}
									{\vlhy {}}}}}}}}
		}$

@@

The proof of $\kax[4]$ shows the need of having the rule corresponding to the frame condition $\rn{F_1}$:

\begin{center}
	$\vlderivation {
		\vlin{\rlabrn{\IMP}}
		{\lb y \mbox{ fresh}}
		{\Rightarrow \labels{x}{(\DIA A \IMP \BOX B) \IMP \BOX (A \IMP B)}}
		{\vlin {\rlabrn{\BOX}}
			{\lb z, \lb w \mbox{ fresh}}
			{\futs xy, \labels{y}{\DIA A \IMP \BOX B} \Rightarrow \labels{y}{\BOX (A \IMP B)}}
			{\vlin {\rlabrn{\IMP}}
				{\lb u \mbox{ fresh}}
				{\futs xy, \futs yz, \accs zw, \labels{y}{\DIA A \IMP \BOX B} \Rightarrow \labels{w}{A \IMP B}}
				{\vlin {\color{red}{\rn{F_1}}}
					{}
					{\futs xy, \futs yz, \futs wu, \accs zw, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}}
					{\vlin {\rn{trans}}
						{}
						{\futs xy, \futs yz, \futs wu, \futs zt, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}}
						{\vliin {\llabrn{\IMP}}
							{}
							{\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}}
							{\vlhy{\circledast  \hspace{75mm}}}
							{\vlhy{\star}}}}}}}
	}$

The derivation continues as the result of applying the rule $\llabrn{\IMP}$. From this rule we obtain two trees:

On one side, the derivation that follows from $\circledast$:

	$
	\vlderivation{
		\vlin{\llabrn{\IMP}}{}{\circledast}{\vlin {\rlabrn{\DIA}}
			{}
			{\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}}
			{\vlin {\rn{refl}}
				{}
				{\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}
				{\vlin {\rn{id}}
					{}
					{\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \futs uu, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}
					{\vlhy {}}}}}
	}$
\end{center}

@@

	$\vlderivation {
		\vlin{\rlabrn{\IMP}}
		{}
		{\Rightarrow \labels{x}{\DIA \BOT \IMP \BOT}}
		{\vlin {\llabrn{\DIA}}
			{}
			{\futs xy, \labels{y}{\DIA \BOT} \Rightarrow \labels{y}{\BOT}}
			{\vlin {\llabrn{\BOT}}
				{}
				{\futs xy, \accs yz, \labels{z}{\BOT} \Rightarrow \labels{y}{\BOT}}
				{\vlhy {}}}}
	}$

@@

\begin{center}
	$\vlderivation {
		\vlin{\rlabrn{\IMP}}
		{}
		{\Rightarrow \labels{x}{A \AND B \IMP B}}
		{\vlin {\llabrn{\AND}}
			{}
			{\futs xy, \labels{y}{A \AND B} \Rightarrow \labels{y}{B}}
			{\vlin {\rn{refl}}
				{}
				{\futs xy, \labels{y}{A}, \labels{y}{B} \Rightarrow \labels{y}{B}}
				{\vlin {\rn{id}}
					{}
					{\futs xy, \futs yy, \labels{y}{A}, \labels{y}{B} \Rightarrow \labels{y}{B}}
					{\vlhy {}}}}}
	}$
\end{center}

\todo{I do not know how to close the theorem}

As we mentioned, in order to conclude the proof of the Theorem~\ref{thm:cutfree-compl} we simulate the necessitation rule and modus ponens.
